Spatial phylogenetics of Japanese ferns: Patterns, processes, and implications for conservation

### 2021-09-22 ms/data_exploration.Rmd
Update MS

The next step uses `tar_load()` to load the dataset from the targets cache. Alternatively, this can be loaded from the dryad data file as shown in the commented-out code below.

@@

# Alternatively, unzip `results.zip` in the Dryad data
# (FIXME: add DOI when available)
# and read in the data from there
# biodiv_ferns_cent_dryad <- read_csv(here::here("japan_ferns_biodiv.csv"))
```

>>>>

The next step uses `tar_load()` to load the dataset from the targets cache. Alternatively, this can be loaded from the data file as shown in the commented-out code below.

@@

# Alternatively, unzip `results.zip`
# (FIXME: add DOI when available)
# and read in the data from there
# biodiv_ferns_cent_dryad <- read_csv(here::here("japan_ferns_biodiv.csv"))
```

### 2021-09-22 ms/manuscript.Rmd
Update MS

Our data include all ferns known to natively occur within the boundaries of Japan . 
Japan (20°N to 45°N, 122°E to 153°E) consists of four main islands and thousands of smaller ones (`r figure("japan-map")`). 
Most of the main islands have been in contact with the continent at various points in the past during periods of lower sea level, but the Ogasawara archipelago consists of oceanic islands that have never been connected to the mainland. 
The climate is subtropical in the south and temperate in other parts of the country. 
Map data for Japan were downloaded from the Geospatial Information Authority of Japan under the Creative Commons Attribution License v4.0 (https://www.gsi.go.jp/kankyochiri/gm_japan_e.html).

@@

We used a list of fern specimens deposited at TNS [herbarium codes follow @Thiers2021]. 
We chose to use this over other sources (e.g., GBIF), because of its high taxonomic quality: all identifications are standardized to a common taxonomy, the Japan Green List v. 1.01 (http://www.rdplants.org/gl/). 
Furthermore, the overall sampling completeness of this dataset is extremely high (`r s_figure("sampling-curve")` in Appendix S1 in Supporting Information). 
The original list comprises `r occ_sum$unfiltered$n_specimens$value %>% scales::number(big.mark = ",")` specimens representing `r occ_sum$unfiltered$n_taxa$value` terminal taxa at the rank of species, subspecies, form, or variety (hereafter referred to as "taxa" unless otherwise indicated), excluding non-native taxa and nothotaxa.
Latitude and longitude of each occurrence record were projected into the Japanese Geodetic Datum 2000 (JGD 2000), which was also used for all further geographic analyses.
We filtered out any occurrences not within a map of standard grid squares defined by the Statistics Bureau of Japan (http://www.stat.go.jp/english/data/mesh/05.html) and removed duplicate collections (`r occ_sum$filtered$n_specimens$value %>% scales::number(big.mark = ",")` specimens, `r occ_sum$filtered$n_taxa$value` taxa after filtering).
The R package `r pack("sf")` was used for all GIS analyses [@Pebesma2018].

@@

Initial inspection of the biodiversity and environmental data showed a single outlier in % apomictic taxa due to extremely low species richness (Appendix S2), so that grid-cell and one grid-cell lacking environmental data were excluded from modeling analyses.

@@

Code to replicate all analyses, figures, and this manuscript are available at https://github.com/joelnitta/japan_ferns_spatial_phy. 
A Docker image to run the code is available at https://hub.docker.com/r/joelnitta/japan_ferns_spatial_phy.
Data files needed to run the analysis and selected results files are available from Figshare at http://doi.org/FIXME:ADD_DOI_HERE_WHEN_ASSIGNED.

@@

# References
<!-- Insert <div id="refs"></div> to place the refs here instead of at the end -->
<div id="refs"></div>

>>>>

Japan (20°N to 45°N, 122°E to 153°E) consists of four main islands and thousands of smaller ones (`r figure("japan-map")`). 
Most of the main islands have been in contact with the continent at various points in the past during periods of lower sea level, but the Ogasawara archipelago consists of oceanic islands that have never been connected to the mainland. 
The climate is subtropical in the southern islands and temperate in other parts of the country. 
Map data for Japan were downloaded from the Geospatial Information Authority of Japan under the Creative Commons Attribution License v4.0 (https://www.gsi.go.jp/kankyochiri/gm_japan_e.html).

@@

We used a list of fern specimens deposited at TNS [herbarium codes follow @Thiers2021]. 
We chose to use this over other sources (e.g., GBIF), because of its high taxonomic quality: all identifications are standardized to a common taxonomy, the Japan Green List v. 1.01 (http://www.rdplants.org/gl/). 
Furthermore, the overall sampling completeness of this dataset is extremely high (`r s_figure("sampling-curve")` in Appendix S1; see Supplemental Data with this article). 
The original list comprises `r occ_sum$unfiltered$n_specimens$value %>% scales::number(big.mark = ",")` specimens representing `r occ_sum$unfiltered$n_taxa$value` terminal taxa at the rank of species, subspecies, form, or variety (hereafter referred to as "taxa" unless otherwise indicated), excluding non-native taxa and nothotaxa.
Latitude and longitude of each occurrence record were projected into the Japanese Geodetic Datum 2000 (JGD 2000), which was also used for all further geographic analyses.
We filtered out any occurrences not within a map of standard grid squares defined by the Statistics Bureau of Japan (http://www.stat.go.jp/english/data/mesh/05.html) and removed duplicate collections (`r occ_sum$filtered$n_specimens$value %>% scales::number(big.mark = ",")` specimens, `r occ_sum$filtered$n_taxa$value` taxa after filtering).
The R package `r pack("sf")` was used for all GIS analyses [@Pebesma2018].

@@

Initial inspection of the biodiversity and environmental data showed a single outlier in % apomictic taxa due to extremely low species richness (Appendix S2; see Supplemental Data with this article), so that grid-cell and one grid-cell lacking environmental data were excluded from modeling analyses.

@@

Code to replicate all analyses, figures, and this manuscript are available at https://github.com/joelnitta/japan_ferns_spatial_phy. 
A Docker image to run the code is available at https://hub.docker.com/r/joelnitta/japan_ferns_spatial_phy.
Data files needed to run the analysis and selected results files are available from Figshare at http://doi.org/10.6084/m9.figshare.16655263.
**Note to reviewers**: the Figshare DOI will not be accessible until the paper is accepted. During review, the data can be accessed from this link: https://figshare.com/s/de3d5a70e118208e56c5.

@@

**Appendix S2**. Exploratory data analysis for spatial modeling.

# Literature cited
<!-- Insert <div id="refs"></div> to place the refs here instead of at the end -->
<div id="refs"></div>
